Notes on the low density parameters in {\tt MAESTRO}

### 2010-04-02 docs/architecture/architecture.tex
add a list of figures

\begin{figure}[h]
\centering
\includegraphics[width=5.0in]{\archfigpath/maestro_directory2}
\caption{The basic MAESTRO directory structure}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=6.5in]{\archfigpath/data_loc2}
\caption{\label{fig:dataloc} Some of the different data-centerings:
  (a) cell-centered, (b) nodal in the $x$-direction, and (c) nodal in
  both the $x$- and $y$-directions.  Note that for nodal data, the
  integer index corresponds to the lower boundary in that direction.
  In each of these centerings, the red point has the same indices:\ (1,2).
  Not shown is the case where data is nodal in the $y$-direction only.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=4.0in]{\archfigpath/index_grid2}
\caption{\label{fig:boxes} Three boxes that comprise a single level.
At this resolution, the domain is 20$\times$18 zones.  Note that the
indexing in BoxLib starts with $0$.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{\archfigpath/mac2}
\hspace{0.1in}
\begin{minipage}[b]{3.8in}
\caption{\label{fig:mac} The MAC grid for the velocity.  
Here the $x$-velocity is on the $x$-edges (shown as the 
blue points) and the $y$-velocity is on the $y$-edges
(shown as the red points).
}\ \\
\end{minipage}
\end{figure}

>>>>

\begin{figure}[h]
\centering
\includegraphics[width=5.0in]{\archfigpath/maestro_directory2}
\caption[MAESTRO directory structure]
{The basic MAESTRO directory structure}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=6.5in]{\archfigpath/data_loc2}
\caption[Data-centerings on the grid]
  {\label{fig:dataloc} Some of the different data-centerings:
  (a) cell-centered, (b) nodal in the $x$-direction, and (c) nodal in
  both the $x$- and $y$-directions.  Note that for nodal data, the
  integer index corresponds to the lower boundary in that direction.
  In each of these centerings, the red point has the same indices:\ (1,2).
  Not shown is the case where data is nodal in the $y$-direction only.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=4.0in]{\archfigpath/index_grid2}
\caption[Single-level grid structure]
{\label{fig:boxes} Three boxes that comprise a single level.  At this
  resolution, the domain is 20$\times$18 zones.  Note that the
  indexing in BoxLib starts with $0$.}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[width=2.5in]{\archfigpath/mac2}
\hspace{0.1in}
\begin{minipage}[b]{3.8in}
\caption[The MAC grid]
{\label{fig:mac} The MAC grid for the velocity.  
Here the $x$-velocity is on the $x$-edges (shown as the 
blue points) and the $y$-velocity is on the $y$-edges
(shown as the red points).
}\ \\
\end{minipage}
\end{figure}

### 2010-04-02 docs/flowchart/flowchart.tex
fix how figures are found
add a list of figures

%-----------------------------------------------------------------------------
% graphical flowcharts
%-----------------------------------------------------------------------------
\begin{figure}[tb]
\centering
\includegraphics[scale=0.6]{flowchart}
\caption{\label{Fig:flowchart} A flowchart of the algorithm.  The
  thermodynamic state variables, base state variables, and local velocity are
  indicated in each step.  Red text indicates that quantity was
  updated during that step.  The predictor-corrector steps are
  outlined by the dotted box.  The blue text indicates state
  variables that are the same in {\bf Step 6} as they are in
  {\bf Step 2}, i.e., they are unchanged by the predictor steps.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                               
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%                                               
\begin{figure}[tb]                                                              
\centering
\includegraphics[scale=0.6]{flowchart_4_8}
\caption{\label{Fig:flowchart48}
A flowchart for {\bf Steps 4} and {\bf 8}.  The thermodynamic state variables
and base state variables are indicated in each step.  Red text indicates that q\
uantity
was updated during that step.  Note, for {\bf Step 4}, the updated
quantities should also have a $\star$ superscript, e.g., {\bf Step 8I} defines
$T^{(2)}$ while {\bf Step 4I} defines $T^{(2),\star}$ .}
\end{figure}

>>>>

%-----------------------------------------------------------------------------
% graphical flowcharts
%-----------------------------------------------------------------------------
\begin{figure}[tb]
\centering
\includegraphics[scale=0.6]{\flowfigpath/flowchart}
\caption[Graphical flowchart of MAESTRO]
  {\label{Fig:flowchart} A flowchart of the algorithm.  The
  thermodynamic state variables, base state variables, and local velocity are
  indicated in each step.  Red text indicates that quantity was
  updated during that step.  The predictor-corrector steps are
  outlined by the dotted box.  The blue text indicates state
  variables that are the same in {\bf Step 6} as they are in
  {\bf Step 2}, i.e., they are unchanged by the predictor steps.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[tb]                                               
\centering
\includegraphics[scale=0.6]{\flowfigpath/flowchart_4_8}
\caption[Graphical flowchart of the density and enthalpy update steps]
{\label{Fig:flowchart48} A flowchart for {\bf Steps 4} and {\bf 8}.
  The thermodynamic state variables and base state variables are
  indicated in each step.  Red text indicates that q\ uantity was
  updated during that step.  Note, for {\bf Step 4}, the updated
  quantities should also have a $\star$ superscript, e.g., {\bf Step
    8I} defines $T^{(2)}$ while {\bf Step 4I} defines $T^{(2),\star}$
  .}
\end{figure}

### 2010-04-02 docs/lo_density/lo_density.tex
update cutoff document to reflect new density floor
add a list of figures

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value (see Figure \ref{Fig:Cutoff}.
We compute the cutoff coordinate at the
coarsest level, and then set the coordinate at the next finer level to be twice that
of the coarser level.  We set the coordinates at the following points in the code:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hpb]
\centering
\includegraphics[width=4.0in]{\lodensfigpath/cutoff}\hspace{0.2in}
\begin{minipage}[b]{5.0in}
\caption{Image of how the cutoff density and cutoff coordinates
are related.  This is drawn assuming {\tt drdxfac}=5.\vspace{2em}}
\end{minipage}
\label{Fig:Cutoff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

>>>>

At several points in the algorithm, we compute {\tt anelastic\_cutoff\_coord}, 
{\tt base\_cutoff\_density\_coord}, and {\tt burning\_cutoff\_density\_coord} by 
setting the corresponding coordinate equal to $r$ as soon as $\rho_0(r)$ is less than 
or equal to that particular cutoff value (see Figure \ref{Fig:Cutoff}.
We compute the cutoff coordinate at the
coarsest level, and then set the coordinate at the next finer level to be twice that
of the coarser level.  We set the coordinates at the following points in the code:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[hpb]
\centering
\includegraphics[width=4.0in]{\lodensfigpath/cutoff}\hspace{0.2in}
\begin{minipage}[b]{5.0in}
\caption[Relation between cutoff density and cutoff coordinates]
{Image of how the cutoff density and cutoff coordinates
are related.  This is drawn assuming {\tt drdxfac}=5.\vspace{2em}}
\end{minipage}
\label{Fig:Cutoff}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\item In {\tt update\_scal}, if $\rho \le {\tt base\_cutoff\_density}/2$
   we set it to ${\tt base\_cutoff\_density}/2$.
